Hybrid Threads for the Parrot Virtual Machine

### 2012-02-21 Paper.tex
Some words about garbage collection

>>>>

A garbage collector has to traverse and process the entire tree of objects in memory. If during this traversal another thread is changing this tree by creating new objects, moving them around in the tree or removing them, the garbage collector's data would be compromised. For example it could happen that the GC does not mark referenced objects alive because they were added to parents which already have been processed.

In previous attempts to implement threading support in Parrot, the answer to this problem was to disable the garbage collector while multiple threads are active. Other VMs solve this problem by suspending all threads while the GC is running.
